---
title: "Chapter 5: Structure Related Analysis"
author: "Longping Fu"
date: "03/20/2025"
output: github_document
---

To perform structure-related analysis of peptide sequences and post-translational modifications, you first need to install two Python packages: [localCIDER](https://pappulab.github.io/localCIDER/) and [StructureMap](https://github.com/MannLabs/structuremap). Please refer to their documentation for installation instructions and usage details.  

Additionally, you can use [Anaconda](https://docs.anaconda.com/anaconda/install/) to set up a virtual environment for managing dependencies efficiently.  

```{r, echo = TRUE}
# import packages
library(tidyverse)
library(reticulate)

# use specific virtual environment you just created
use_condaenv(
  condaenv = '/opt/anaconda3/envs/structure_analysis',
  required = TRUE
)

```

```{r, echo = TRUE}
# execute the python script for structure analysis
source_python("structure_analysis.py")

```

```{r, echo = TRUE}
## check the result
# peptide physicochemical property analysis
HEK_Nterm_Kd_half_life_sequence |> 
  as_tibble() |> 
  head(10)

# protein modification structure analysis
common_Nterm_alphafold_N_terminus |>
  as_tibble() |>
  head(10)

enrichment_N_terminus |>
  as_tibble() |>
  head(10)

common_Nterm_proximity |>
  as_tibble() |>
  head(10)

```

```{r, echo = TRUE}
sessionInfo()
```
